---
title: "Assessing timeframes"
author: "Natalia Petersen"
date: "2025-01-02"
output: html_document

knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "N:/INFO/_LIVE/NCIN/Treatment Flags/Treatments data 2022/Bladder resection/"
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
```


```{r install packages, include=FALSE}

library(NDRSAfunctions) #install via instructions here https://github.com/NHSE-NDRS/NDRSAfunctions
library(dplyr)
library(ggplot2)
library(openxlsx2)
library(tidyverse)
```

```{r set parameters, include = FALSE}

# Set the snapshot and schema
avyyyy <- "av2022"
snapshot <- "cas2501l" #for springmvc3.ZOPCS table
CAS_username <- "analysischarlotteeversfield"

# Cancer site name
cancer_site = 'bladder_cancer'

# Define cancer site
use_tumour_cohort = FALSE #specify if you want to use the tr tumour cohort table, or create a new cohort

#site_definition = "tumour_code = 'Uncertain/unknown or other bladder'"
site_definition = "site_icd10_o2_3char in ('C67')"

# Set the diagnosis years 
min_diagnosis_year<-"2016"
max_diagnosis_year<-"2022"

# Set resection list filename - these should have been agreed with the clinician
resection_list <- r"(Potentially_relevant_bladder_cancer_resections_v0.0.xlsx)"

# Set filepath to save data:
output_filepath = r"(N:\INFO\_LIVE\NCIN\Treatment Flags\Treatments data 2022\Bladder resection\)"

# Set whether want to drop previous cohort table - TRUE/FALSE
drop_cohort_table = TRUE

```

```{r set plot output file names, include = FALSE}

# Set output names
output_plot_sg = paste0(cancer_site, "_timeframes_sg.png")
output_plot_ct = paste0(cancer_site, "_timeframes_ct.png")
output_plot_rt = paste0(cancer_site, "_timeframes_rt.png")

```

```{r connect to CAS, include = FALSE}
#Create CAS connection with casref02
CAS_casref02 = createConnection(sid = "CASREF02", username = CAS_username)
```

```{r read in surgery codes, include = FALSE}

# Surgery codes
# Reads in the relevant surgery codes agreed with the clinician, including only those flagged as 'y'
surgery_list <- read_xlsx(paste0(output_filepath,resection_list))
surgery_codes <- surgery_list %>%
  mutate(RELEVANT_SURGERY_CODE = toupper(RELEVANT_SURGERY_CODE)) %>% # Capitalise all values
  filter(substr(RELEVANT_SURGERY_CODE, 1, 1) == "Y") # Check the first character

# format surgery codes list
surgery_codes <- shQuote(surgery_codes$OPERTN) # adds quotation marks
surgery_codes_list <- paste0(surgery_codes, collapse = ', ') # adds commas
surgery_codes_list <- gsub('"', "'", surgery_codes_list) # changes to single quotes


```


This script should be used to define treatment timeframes for a specific cancer site, for surgery, chemotherapy, and radiotherapy. This is primarily used for the routine publication on cancer treatments from the National Disease Registration Service: [cancer treatments](https://digital.nhs.uk/ndrs/data/data-outputs/cancer-data-hub/cancer-treatments). These plots should be reviewed by and developed in consultation with experienced site-specific clinicians.  

This script will extract treatment data and filter to 1 month before diagnosis to 2 years after diagnosis for the cancer site of interest. These are then plotted to present the point at which 95% of the treated cohort had received the specified treatment.

Although this step requires a data-driven approach, these plots should be shared with a site-specific clinician to gain clinical expertise on how this compares to their experience in clinical practice.

This script should be run following the definition of surgery codes using the *Assessing OPCS surgery codes* script to define the relevant excision codes. 


```{r create cohort data, include = FALSE}

if(drop_cohort_table == TRUE){
dbSendQueryOracle(CAS_casref02, paste0("drop table ",cancer_site,"_cohort_table purge"))
}

if(use_tumour_cohort == TRUE){
  
  dbSendQueryOracle(CAS_casref02, 
paste0("create table ",cancer_site,"_cohort_table as
select tumourid, patientid, nhsnumber, diagnosisdatebest
FROM tr_tumour_cohort AVT 
WHERE ",site_definition," 
AND extract(year from avt.diagnosisdatebest) between ",min_diagnosis_year," and ",max_diagnosis_year,"
"))
  
} else {
  
  dbSendQueryOracle(CAS_casref02, 
paste0("create table ",cancer_site,"_cohort_table as
select tumourid, patientid, nhsnumber, diagnosisdatebest
FROM ",avyyyy,".at_tumour_england@casref02 AVT 
WHERE ",site_definition," 
AND avt.diagnosisyear between ",min_diagnosis_year," and ",max_diagnosis_year,"
AND avt.ctry_code = 'E'
AND avt.statusofregistration = 'F'
AND avt.dedup_flag = '1'
AND avt.age BETWEEN 0 AND 200
"))

  }


```


## Assessing surgeries timeframes


```{r surgery data extract, echo=FALSE, warning=FALSE}

# AV.treatment
av_treat<-dbGetQueryOracle(CAS_casref02, 
paste0("select opertn
,obs_resect_time
,count(distinct tumourid)
from (select opcs4_code as opertn
, (avtreat.eventdate-tc.diagnosisdatebest) as obs_resect_time
, RANK() OVER (PARTITION BY tc.tumourid ORDER BY avtreat.eventdate, avtreat.eventid) AS rk 
, tc.tumourid
from ",cancer_site,"_cohort_table tc
INNER JOIN ",avyyyy,".at_treatment_england@casref02 avtreat ON avtreat.tumourid=tc.tumourid 
AND eventcode IN ('01a','01b','01z', '01c')
where avtreat.opcs4_code in (",surgery_codes_list,")
AND (avtreat.eventdate-tc.diagnosisdatebest BETWEEN -31 AND 730) 
)
WHERE rk=1
group by obs_resect_time, opertn"))


#HES
HES_treat<-dbGetQueryOracle(CAS_casref02, 
paste0("select opertn
,obs_resect_time
,count(distinct tumourid)
from (select opertn
, (ho.opdate-tc.diagnosisdatebest) as obs_resect_time
,RANK() OVER (PARTITION BY tc.tumourid ORDER BY ho.opdate, hl.datayear,hl.epikeyanon,POS) AS rk 
, tc.tumourid
from ",cancer_site,"_cohort_table tc
INNER JOIN heslive.hes_linkage_av_apc@casref02 hl ON tc.patientid = hl.patientid 
INNER JOIN heslive.hesapc_opertn@casref02 ho ON ho.datayear = hl.datayear AND ho.epikeyanon = hl.epikeyanon 
INNER JOIN heslive.hesapc@casref02 ha ON ha.datayear = hl.datayear AND ha.epikeyanon = hl.epikeyanon 
where ho.opertn in (",surgery_codes_list,")
AND (ho.opdate-tc.diagnosisdatebest BETWEEN -31 AND 730) 
)
WHERE rk=1
group by obs_resect_time, opertn

union all

select opertn
,obs_resect_time
,count(distinct tumourid)
from (select opertn
, (op.apptdate-tc.diagnosisdatebest) as obs_resect_time
,RANK() OVER (PARTITION BY tc.tumourid ORDER BY op.apptdate, h2.datayear,h2.attendkeyanon,POS) AS rk 
, tc.tumourid
from ",cancer_site,"_cohort_table tc
INNER JOIN heslive.hes_linkage_av_op@casref02 h2 ON tc.patientid = h2.patientid
INNER JOIN heslive.hesop_opertn@casref02 ho2 ON ho2.datayear = h2.datayear AND ho2.attendkeyanon = h2.attendkeyanon
INNER JOIN heslive.hesop@casref02 op ON op.datayear = h2.datayear and op.attendkeyanon = h2.attendkeyanon 
where ho2.opertn in (",surgery_codes_list,")
AND (op.apptdate-tc.diagnosisdatebest BETWEEN -31 AND 730)
)
WHERE rk=1
group by obs_resect_time, opertn
"))

```


```{r surgery data for plotting, echo=FALSE}

# Merge av_treat and HES data together
treat_data<-rbind(av_treat,HES_treat)

#numerator = number of treatments by days from diagnosis
#denominator = total resections in 2 years
treat_data<- treat_data %>%
  group_by(OBS_RESECT_TIME) %>%
  summarize("count" = sum(`COUNT(DISTINCTTUMOURID)`))%>%
  mutate(denom=sum(count),
         pct=(cumsum(count)/sum(count))*100)
```


```{r sg plots, echo=FALSE, warnings = FALSE}

treat_data<-treat_data|>
  filter(!OBS_RESECT_TIME==0)

site_plot_sg<-ggplot(treat_data, aes(x=OBS_RESECT_TIME, y=pct, group=1)) +
  geom_line(colour="#238789",size=1)+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "gray10", fill=NA, size=0.5),
        panel.background = element_rect(fill = "white", color = NA),  # White panel background
    plot.background = element_rect(fill = "white", color = NA)   # White plot background
    )+
  ggtitle(label = paste0("Number of days between diagnosis and resections in AV treatment, HESAPC and \nHESOP")) +
  ylab("Percentage of resections") + 
  xlab("Days from diagnosis")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size =8))+
  scale_y_continuous(labels=function(x) format(x, big.mark = ",", scientific = FALSE),breaks = scales::pretty_breaks(n = 10))+
  scale_x_continuous(limits=c(-31, 750),
                     breaks=c(seq(-31,750, by=30)),expand = c(0,0))+
  geom_hline(yintercept =95, linetype="dashed")

print(site_plot_sg)
  
point_95<-filter(treat_data,round(pct,0)==95)
if (nrow(point_95) == 0) {
  point_95 <- treat_data %>%
    slice(which.min(abs(pct - 95))) # If no rows round to 95, select the row with pct closest to 95
}
time_point<-(min(point_95$OBS_RESECT_TIME)/30.5)
time_point <- round(time_point, digits = 2) # make to 2dp

# Round to the nearest 3-month interval
rounded_months <- ceiling(time_point / 3) * 3

if (rounded_months < 6) {
  rounded_months <- 6
} else if (rounded_months > 15) {
  rounded_months <- 15
}

```

The 95% point for surgeries is at `r paste0(time_point)` months (`r paste0(round(min(point_95$OBS_RESECT_TIME)))` days).

To the nearest 3-months, this would be `r paste0(rounded_months)` months.


```{r sg export data, echo=FALSE}

# Graph export
ggsave(filename = paste0(output_filepath,output_plot_sg), plot = site_plot_sg, width = 8, height = 6, dpi = 300)

```


## Assessing chemotherapy timeframes


```{r ct data extract, echo=FALSE}

av_treat_ct<-dbGetQueryOracle(CAS_casref02, paste0(
"select obs_ct_time, count(distinct tumourid)
from(select (avtreat.eventdate-tc.diagnosisdatebest) as obs_ct_time
, RANK() OVER (PARTITION BY tc.tumourid ORDER BY avtreat.eventdate, avtreat.eventid) AS rk 
,  tc.tumourid
from ",cancer_site,"_cohort_table tc
INNER JOIN ",avyyyy,".at_treatment_england@casref02 avtreat ON avtreat.tumourid=tc.tumourid 
AND eventcode IN ('02','04','15','CTX') 
AND (avtreat.eventdate-tc.diagnosisdatebest BETWEEN -31 AND 730)
) where rk=1
group by obs_ct_time
"))


sact1_ct<-dbGetQueryOracle(CAS_casref02, paste0(
"select obs_ct_time, count(distinct tumourid)
from(select (sr.start_date_of_regimen-tc.diagnosisdatebest) as obs_ct_time
,RANK() OVER (PARTITION BY tc.tumourid ORDER BY sr.start_date_of_regimen, sr.merged_regimen_id, st.merged_tumour_id) AS rk 
,  tc.tumourid
from ",cancer_site,"_cohort_table tc
INNER JOIN sact_legacy.patient@casref02 sp ON tc.nhsnumber=sp.nhs_number 
INNER JOIN sact_legacy.tumour@casref02 st ON sp.merged_patient_id=st.merged_patient_id 
INNER JOIN sact_legacy.regimen@casref02 SR on st.merged_tumour_id=sr.merged_tumour_id 
AND (NOT (benchmark_group IN ('NOT CHEMO','HORMONES','ZOLEDRONIC ACID','PAMIDRONATE','DENOSUMAB', 'RADIUM 223', 'LUTETIUM-177', 'YTTRIUM-90') OR benchmark_group IS NULL)) 
AND sr.start_date_of_regimen<=TO_DATE('2017-06-30','YYYY-MM-DD')
AND (sr.start_date_of_regimen-tc.diagnosisdatebest BETWEEN -31 AND 730)
) where rk=1
group by obs_ct_time
"))


sact2_ct<-dbGetQueryOracle(CAS_casref02, paste0(
"select obs_ct_time, count(distinct tumourid)
from(select (sr.start_date_of_regimen-tc.diagnosisdatebest) as obs_ct_time
,RANK() OVER (PARTITION BY tc.tumourid ORDER BY sr.start_date_of_regimen, sr.merged_regimen_id, st.sact_tumour_id) AS rk
, tc.tumourid
from ",cancer_site,"_cohort_table tc
INNER JOIN sact.at_patient_england@",snapshot," sp ON tc.nhsnumber=sp.nhs_number 
INNER JOIN sact.at_tumour_england@",snapshot," st ON sp.encore_patient_id = st.encore_patient_id
INNER JOIN sact.at_regimen_england@",snapshot," sr ON st.sact_tumour_id=sr.sact_tumour_id 
AND (NOT (benchmark_group IN ('NOT CHEMO','HORMONES','ZOLEDRONIC ACID','PAMIDRONATE','DENOSUMAB', 'RADIUM 223', 'LUTETIUM-177', 'YTTRIUM-90') OR benchmark_group IS NULL))
AND sr.start_date_of_regimen>=TO_DATE('2017-07-01','YYYY-MM-DD')
AND (sr.start_date_of_regimen-tc.diagnosisdatebest BETWEEN -31 AND 730) 
) where rk=1
group by obs_ct_time
"))

hes_ct<-dbGetQueryOracle(CAS_casref02, paste0("select obs_ct_time
,count(distinct tumourid)
from (select (ho.opdate-tc.diagnosisdatebest) as obs_ct_time
,RANK() OVER (PARTITION BY tc.tumourid ORDER BY ho.opdate, hl.datayear,hl.epikeyanon,POS) AS rk 
, tc.tumourid
from ",cancer_site,"_cohort_table tc
INNER JOIN heslive.hes_linkage_av_apc@casref02 hl ON tc.patientid = hl.patientid 
INNER JOIN heslive.hesapc_opertn@casref02 ho ON ho.datayear = hl.datayear AND ho.epikeyanon = hl.epikeyanon 
INNER JOIN heslive.hesapc@casref02 ha ON ha.datayear = hl.datayear AND ha.epikeyanon = hl.epikeyanon 
where ho.opertn in ('Y123','X962','X749','X748','X739','X738','X731','X729','X728','X724','X723','X722','X721','X719','X718',
'X715','X714','X713','X712','X711','X709','X708','X705','X704','X703','X702','X701','X385','X384','X374','X373','X353','X352',
'T482','T133','A106')
AND (ho.opdate-tc.diagnosisdatebest BETWEEN -31 AND 730) 
)
WHERE rk=1
group by obs_ct_time

union all

select obs_ct_time
,count(distinct tumourid)
from (select (op.apptdate-tc.diagnosisdatebest) as obs_ct_time
,RANK() OVER (PARTITION BY tc.tumourid ORDER BY op.apptdate, h2.datayear,h2.attendkeyanon,POS) AS rk 
, tc.tumourid
from ",cancer_site,"_cohort_table tc
INNER JOIN heslive.hes_linkage_av_op@casref02 h2 ON tc.patientid = h2.patientid
INNER JOIN heslive.hesop_opertn@casref02 ho2 ON ho2.datayear = h2.datayear AND ho2.attendkeyanon = h2.attendkeyanon
INNER JOIN heslive.hesop@casref02 op ON op.datayear = h2.datayear and op.attendkeyanon = h2.attendkeyanon 
where ho2.opertn in ('Y123','X962','X749','X748','X739','X738','X731','X729','X728','X724','X723','X722','X721','X719','X718',
'X715','X714','X713','X712','X711','X709','X708','X705','X704','X703','X702','X701','X385','X384','X374','X373','X353','X352',
'T482','T133','A106')
AND (op.apptdate-tc.diagnosisdatebest BETWEEN -31 AND 730) 
)
WHERE rk=1
group by obs_ct_time
"))


```

```{r ct merge and filter data, echo=FALSE}

# Merge together
ct_data<-rbind(av_treat_ct,sact1_ct,sact2_ct,hes_ct)


#numerator = number of treatments by days from diagnosis
#denominator = total resections in 2 years
ct_data_filtered<- ct_data %>%
  group_by(OBS_CT_TIME) %>%
  summarize("count" = sum(`COUNT(DISTINCTTUMOURID)`))%>%
  mutate(denom=sum(count),
         pct=(cumsum(count)/sum(count))*100)
```



```{r ct plots, echo=FALSE, warnings = FALSE}

site_plot_ct<-ggplot(ct_data_filtered, aes(x=OBS_CT_TIME, y=pct, group=1)) +
  geom_line(colour="#238789",size=1)+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "gray10", fill=NA, size=0.5),
        panel.background = element_rect(fill = "white", color = NA),  # White panel background
    plot.background = element_rect(fill = "white", color = NA)   # White plot background
    )+
  ggtitle(label = paste0("Number of days between diagnosis and CT in AV treatment, SACT and HES")) +
  ylab("Percentage of CT treatments") + 
  xlab("Days from diagnosis")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size =8))+
  scale_y_continuous(labels=function(x) format(x, big.mark = ",", scientific = FALSE),breaks = scales::pretty_breaks(n = 10))+
  scale_x_continuous(limits=c(-31, 750),
                     breaks=c(seq(-31,750, by=30)),expand = c(0,0))+
  geom_hline(yintercept =95, linetype="dashed")

print(site_plot_ct)

point_95<-filter(ct_data_filtered,round(pct,0)==95)
if (nrow(point_95) == 0) {
  point_95 <- ct_data_filtered %>%
    slice(which.min(abs(pct - 95))) # If no rows round to 95, select the row with pct closest to 95
}
time_point<-(min(point_95$OBS_CT_TIME)/30.5)
time_point <- round(time_point, digits = 2) # make to 2dp

# Round to the nearest 3-month interval
rounded_months <- ceiling(time_point / 3) * 3

if (rounded_months < 6) {
  rounded_months <- 6
} else if (rounded_months > 18) {
  rounded_months <- 18
}

```

The 95% point for chemotherapy is at `r paste0(time_point)` months (`r paste0(round(min(point_95$OBS_CT_TIME)))` days).

To the nearest 3-months, this would be `r paste0(rounded_months)` months.

```{r ct export data, echo=FALSE}

# Graph export
ggsave(filename = paste0(output_filepath,output_plot_ct), plot = site_plot_ct, width = 8, height = 6, dpi = 300)

```



## Assessing radiotherapy timeframes


```{r rt data extract, echo=FALSE}

av_treat_rt<-dbGetQueryOracle(CAS_casref02, paste0(
                              "select obs_rt_time, count(distinct tumourid)
from(select (avtreat.eventdate-tc.diagnosisdatebest) as obs_rt_time
, RANK() OVER (PARTITION BY tc.tumourid ORDER BY avtreat.eventdate, avtreat.eventid) AS rk 
,  tc.tumourid
from ",cancer_site,"_cohort_table tc 
INNER JOIN ",avyyyy,".at_treatment_england@casref02 avtreat ON avtreat.tumourid=tc.tumourid 
AND eventcode IN ('04','05', '06', '22','RTX', '19')
AND (avtreat.eventdate-tc.diagnosisdatebest BETWEEN -31 AND 730)
) where rk=1
group by obs_rt_time
"))


rtds1_rt<-dbGetQueryOracle(CAS_casref02, paste0(
                           "select obs_rt_time, count(distinct tumourid)
from(select (rl.apptdate-tc.diagnosisdatebest) as obs_rt_time
,RANK() OVER (PARTITION BY tc.tumourid ORDER BY rl.apptdate,rl.attendid,rl.orgcodeprovider,pr.radiotherapyepisodeid,pr.prescriptionid) AS rk 
,  tc.tumourid
from ",cancer_site,"_cohort_table tc
INNER JOIN rtds2016.opcds_cas1712_linkage rl ON tc.patientid=rl.patientid
INNER JOIN rtds2016.rtds_prescriptions pr ON pr.orgcodeprovider = rl.orgcodeprovider AND pr.attendid = rl.attendid 
AND pr.apptdate = rl.apptdate
AND (rl.apptdate-tc.diagnosisdatebest BETWEEN -31 AND 730)
) where rk=1
group by obs_rt_time
"))


rtds2_rt<-dbGetQueryOracle(CAS_casref02, paste0(
                           "select obs_rt_time, count(distinct tumourid)
from(select (pr.apptdate-tc.diagnosisdatebest) as obs_rt_time
,RANK() OVER (PARTITION BY tc.tumourid ORDER BY TO_DATE(pr.apptdate),pr.attendid,pr.orgcodeprovider,pr.radiotherapyepisodeid,pr.prescriptionid) AS rk 
, tc.tumourid
from ",cancer_site,"_cohort_table tc
INNER JOIN rtds.at_prescriptions_england@",snapshot," pr ON pr.patientid=tc.patientid
AND pr.orgcodeprovider <>'7A3' 
AND TO_DATE(pr.apptdate) >= TO_DATE('01-APR-16', 'dd-mm-yy') 
AND (pr.apptdate-tc.diagnosisdatebest BETWEEN -31 AND 730)
) where rk=1
group by obs_rt_time
"))

```

```{r rt merge and filter data, echo=FALSE}

# Merge together
rt_data<-rbind(av_treat_rt,rtds1_rt,rtds2_rt)


#numerator = number of treatments by days from diagnosis
#denominator = total resections in 2 years
rt_data_filtered<- rt_data %>%
  group_by(OBS_RT_TIME) %>%
  summarize("count" = sum(`COUNT(DISTINCTTUMOURID)`))%>%
  mutate(denom=sum(count),
         pct=(cumsum(count)/sum(count))*100)
```



```{r rt plots, echo=FALSE, warnings = FALSE}

site_plot_rt<-ggplot(rt_data_filtered, aes(x=OBS_RT_TIME, y=pct, group=1)) +
  geom_line(colour="#238789",size=1)+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "gray10", fill=NA, size=0.5),
        panel.background = element_rect(fill = "white", color = NA),  # White panel background
    plot.background = element_rect(fill = "white", color = NA)   # White plot background
    )+
  ggtitle(label = paste0("Number of days between diagnosis and RT in AV treatment and RTDS")) +
  ylab("Percentage of RT treatments") + 
  xlab("Days from diagnosis")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size =8))+
  scale_y_continuous(labels=function(x) format(x, big.mark = ",", scientific = FALSE),breaks = scales::pretty_breaks(n = 10))+
  scale_x_continuous(limits=c(-31, 750),
                     breaks=c(seq(-31,750, by=30)),expand = c(0,0))+
  geom_hline(yintercept =95, linetype="dashed")

print(site_plot_rt)

point_95<-filter(rt_data_filtered,round(pct,0)==95)
if (nrow(point_95) == 0) {
  point_95 <- rt_data_filtered %>%
    slice(which.min(abs(pct - 95))) # If no rows round to 95, select the row with pct closest to 95
}
time_point<-(min(point_95$OBS_RT_TIME)/30.5)
time_point <- round(time_point, digits = 2) # make to 2dp

# Round to the nearest 3-month interval
rounded_months <- ceiling(time_point / 3) * 3

if (rounded_months < 6) {
  rounded_months <- 6
} else if (rounded_months > 18) {
  rounded_months <- 18
}

```

The 95% point for radiotherapy is at `r paste0(time_point)` months (`r paste0(round(min(point_95$OBS_RT_TIME)))` days).

To the nearest 3-months, this would be `r paste0(rounded_months)` months.

```{r rt export data, echo=FALSE}

# Graph export
ggsave(filename = paste0(output_filepath,output_plot_rt), plot = site_plot_rt, width = 8, height = 6, dpi = 300)

```




